Notes on Validated Model Counting \\ Version of \today

### 2022-09-16 doc/mc-notes.tex
Updated document

\begin{table}
  \caption{Encodings of the ITE Operation}
  \label{tab:ite}
  \begin{center}
  \begin{tabular}{ccc}
    ITE Form & & Encoding \\
    \midrule
     $\ite(P_1, P_2, P_3)$ & $\;$ & $(P_1 \pand P_2) \por (\neg P_1 \land P_3)$ \\
     $\ite(\tautology, P_2, P_3)$ & $\;$ & $P_2$ \\
     $\ite(\nil, P_2, P_3)$ & $\;$ & $P_3$ \\
     $\ite(P_1, P_2, P_2)$  & $\;$ & $P_2$ \\
     $\ite(P_1, \tautology, \nil)$ & $\;$ & $P_1$ \\
     $\ite(P_1, \nil, \tautology)$ & $\;$ & $\neg P_1$ \\
     $\ite(P_1, P_2, \nil)$ & $\;$ & $P_1 \pand P_2$ \\
     $\ite(P_1, \nil, P_3)$ & $\;$ & $\neg P_1 \pand P_3$ \\
     $\ite(P_1, \tautology, P_3)$ & $\;$ & $\neg (\neg P_1 \pand \neg P_3)$ \\
     $\ite(P_1, P_2, \tautology)$ & $\;$ & $\neg (P_1 \pand \neg P_2)$ \\

@@

\subsection{TO-DO List}

\begin{itemize}
\item Proof Framework
  \begin{itemize}
  \item Generalities and details of the format
  \item Can some form of abstraction be incorporated?
    \begin{itemize}
    \item Want to abstract a subformula to consider only on its cost and dependency set
    \item Could represent with fresh extension variable
    \item But how to prove logical equivalence?
    \end{itemize}
  \end{itemize}

\item Checker
  \begin{itemize}
  \item Working prototype
  \item C/C++ (or Rust?)
  \item Formally verified
  \end{itemize}

\item Counters
\begin{itemize}
\item BDD-based
  \begin{itemize}
  \item Prototype
  \item C/C++
  \end{itemize}

  \item SDD-based
  \begin{itemize}
  \item Bottom-up
  \item Top-down
  \end{itemize}

\item Others?
\end{itemize}
\end{itemize}

>>>>

\begin{table}
  \caption{Encodings of the ITE Operation}
  \label{tab:ite}
  \begin{center}
  \begin{tabular}{ccc}
    ITE Form & & Encoding \\
    \midrule
     $\ite(P_1, P_2, P_3)$ & $\;$ & $(P_1 \pand P_2) \por (\neg P_1 \land P_3)$ \\
     $\ite(\tautology, P_2, P_3)$ & $\;$ & $P_2$ \\
     $\ite(\nil, P_2, P_3)$ & $\;$ & $P_3$ \\
%     $\ite(P_1, P_2, P_2)$  & $\;$ & $P_2$ \\
     $\ite(P_1, \tautology, \nil)$ & $\;$ & $P_1$ \\
     $\ite(P_1, \nil, \tautology)$ & $\;$ & $\neg P_1$ \\
     $\ite(P_1, P_2, \nil)$ & $\;$ & $P_1 \pand P_2$ \\
     $\ite(P_1, \nil, P_3)$ & $\;$ & $\neg P_1 \pand P_3$ \\
     $\ite(P_1, \tautology, P_3)$ & $\;$ & $\neg (\neg P_1 \pand \neg P_3)$ \\
     $\ite(P_1, P_2, \tautology)$ & $\;$ & $\neg (P_1 \pand \neg P_2)$ \\

@@

\section{Exploiting Shared Subgraphs}

\begin{figure}
\begin{verbatim}
p cnf 4 5
-1 3 -4 0
-1 -3 4 0
1 3 -4 0
1 -3 4 0
-1 -2 0
\end{verbatim}
\caption{CNF representation of Formula \#4}
\label{fig:eg4:cnf}
\end{figure}

\begin{figure}
\begin{verbatim}
c Node P5 = AND(var-3, var-4)
12 p 5 3 4 0
c Node P6 = AND(-var-3, -var-4)
15 p 6 -3 -4 0
c Node S7 = OR(P5, P6)
18 s 7 5 6 13 16 0
c Node P9 = AND(var-1, -var-2, S7)
21 p 9 1 -2 7 0
c Node P10 = AND(-var-1, S7)
25 p 10 -1 7 0
c Node S11 = OR(P9, P10)
28 s 11 9 10 22 26 0
\end{verbatim}
\caption{Declarations of operations to represent Formula \#4}
\label{fig:eg4:ops}
\end{figure}

\begin{figure}
  \centering{
    \centering{\input{dd/eg4}}
  }
\caption{POG for Formula \#4 yielding shared subgraph $s_7$}
\label{fig:eg4:pog}
\end{figure}

\begin{figure}
\begin{verbatim}
c Shadow clause [3, -4]
6 p 12 -3 4 0
c Implicit declarations:
c 6 a 12 3 -4 0
c 7 a -12 -3 0
c 8 a -12 4 0
c Shadow clause [-3, 4]
9 p 13 3 -4 0
c Implicit declarations:
c 9 a 13 -3 4 0
c 10 a -13 3 0
c 11 a -13 -4 0
\end{verbatim}
\caption{Declarations of operations to represent lemma arguments}
\label{fig:eg4:args}
\end{figure}

\begin{figure}
\begin{verbatim}
c Proof of Lemma S7
31 a 12 13 -3 4 0 * 0
32 a 12 13 3 -4 0 * 0
33 a -3 7 12 13 0 31 12 19 0
34 a 7 12 13 0 33 32 15 20 0
c Apply Lemma S7.  Context = [1, -2]
35 a -1 2 -12 0 7 8 1 0
36 a -1 2 -13 0 10 11 2 0
37 a -1 2 7 0 35 36 34 0
c Apply Lemma S7.  Context = [-1]
38 a 1 -12 0 7 8 3 0
39 a 1 -13 0 10 11 4 0
40 a 1 7 0 38 39 34 0
c Assert ITE at node S11 (root)
41 a -1 11 0 5 37 21 29 0
42 a 11 0 41 40 25 30 0
\end{verbatim}
\caption{Assertions leading to unit clause for $t=s_7$}
\label{fig:eg4:assert}
\end{figure}

\begin{figure}
\begin{verbatim}
c Delete all but final asserted clause
dc 41 5 37 21 29 0
dc 40 38 39 34 0
dc 39 10 11 4 0
dc 38 7 8 3 0
dc 37 35 36 34 0
dc 36 10 11 2 0
dc 35 7 8 1 0
dc 34 33 32 15 20 0
dc 33 31 12 19 0
dc 32 * 0
dc 31 * 0
c Delete input clauses
dc 1 13 17 18 24 26 28 42 0
dc 2 14 16 18 24 26 28 42 0
dc 3 22 13 17 18 27 28 42 0
dc 4 22 14 16 18 27 28 42 0
dc 5 23 26 28 42 0
\end{verbatim}
\caption{Clause deletions for Formula \#4}
\label{fig:eg4:delete}
\end{figure}
